---
title: "Assignment 2"
author: "Frank Moeller"
---

# Remaining Questions

# Assignment 2

## Concept

-   2 actors interact (interaction function) exchange their wealth (transaction function)

## Implementation

### Initial Population distribution

```{r}
N<- 5000 # define N as default population size

MU<- 100 # define MU as the default population mean

population <- rnorm(N, mean = MU_1, sd = MU/5) # define the dataframe "population" as a normally distributed set of size "N" (5000) with a mean "M" (100$) and a sd of "MU/5" (20$) 

##is this a dataframe?
```

-   Gaussian (normal) distribution

-   dependent variable = simoleons (\$)

### Visualization

#### Measure

-   Gini coefficient (measure of equality)

    -   0=equality

    -   1=inequality

    -   ! Usually assessed for income, here wealth

```{r}
gini<- function(y) { 
# measure of equality (0=equality, 1=inequality) applied for wealth [usually for income]
y<- sort(y) #puts vector (wealth) of the dataframe in order
n<- length(y) #assess the lenght of the vector (individuals) in the dataframe 
## Question does length define the number of individuals?
numer<- 2*sum((1:n)*y)#defines the numerator of the formular
#sum(start value:end value)
#summs the sorted vecotr (wealth) of the dataframe and multiplies by 2

denom<- n*sum(y)#defines the denominator of the formular
#multiplies the number of participants by the sum of the wealth  

return ((numer/denom)-(n+1)/n)
#puts the formula together
}
```

#### Apply

```{r}
gini(population)
```

reference output: \~0.113

#### Define hist

```{r}
#install.packages("ggplot2")
library(ggplot2)
hist_custom<- function(popuation, label = 'pop',...) {
label <- paste0(label,": G", round(gini(population), 2))
# add and calculate the little gini coefficient in the top right corner

population_df<- data.frame(population = population)
#

ggplot(population_df, aes(x = population))+
  geom_histogram(bin=30,fill='blue',alpha=0.5,...)+
  labs(title=label,x='Wealth',y='Count')+
  theme_minimal()+
  theme(legend.position="none")
}
```

#### Visualize

```{r}
hist_custom(population)
```
